A Wide-Coverage Symbolic Natural Language Inference System

### 2019-07-16 paper2018/paper.tex
remove duplicate reference

\begin{abstract}
  We present a system for Natural Language Inference which uses a
  dynamic semantics converter from abstract syntax trees to Coq
  types. It combines the fine-grainedness of a dynamic semantics
  system with the powerfulness of a state-of-the-art proof assistant. We evaluate the system on all sections of the FraCaS test
  suite, excluding section 6. This is the first system that does a
  complete run on the anaphora and ellipsis sections of the FraCaS. It
  has a better overall accuracy than any previous system.
\end{abstract}
\section{Introduction}
Natural Language Inference (NLI) is the task of determining of whether
an NL hypothesis H follows from an NL premise(s) P. NLI has received a
lot of attention in the Computational Semantics literature and has
been approached using a variety of techniques, ranging from logical
approaches
\citep{bos:2008,Mineshima:2015,Abzianidze:2015,bernardy_type_2017},
all the way to the recent Deep Learning (DL) models for NLI. The
latter approaches, following a general trend in NLP, have been
dominating NLI and a number of impressive results have been
produced \citep{kim:2018,radford:2018,liu:2019}.\footnote{These are
  the three systems with the best results on SNLI in increasing
  order at the time of writing.}  State-of-the-art DL systems achieve an accuracy of around
0.9 when tested on suitable datasets. However, the datasets that are
used are assuming a definition of inference that can be thought to be
`looser' or less precise compared to the definition assumed in
platforms based in logical approaches \citep{bernardy:2019}. For example, consider the following
 example  from the SNLI dataset, predominatly used to test DL
approaches:
%
\begin{lingex}
\item % An SNLI example \\
  \label{ex:snli}
\textbf{P}  A  man selling donuts to a customer during a world
exhibition event held in the city of Angeles. \\
 \textbf{H}  A woman drinks her coffee in a small cafe.\\
\textbf{Label: Contradiction} [SNLI]
% \item % An example from FraCaS\\
% \textbf{P1} A Scandinavian won the Nobel Prize.\\
% \textbf{P2}	Every Swede is  Scandinavian.\\
% \textbf{Q}  Did a Swede win the Nobel prize? \\
% \textbf{H} A Swede won the Nobel prize.\\
% \textbf{Label: Yes} [FraCaS 173]
\end{lingex}
%
In \ref{ex:snli}, a number of non-trivial
assumptions have to be made in order to arrive at a contradiction: a) the two
situations described have to be taken to refer to the same situation
in order to judge that the latter  contradicts the former, b)
the indefinite article in the premise has to be identified with the
indefinite article in the hypothesis. (Additionally considering that a
person cannot be a man selling donuts and a woman drinking coffee at
the same time.) While this can be part of the reasoning humans
perform, it is not the only possibility. More precise, logical
reasoning is also a possibility, and will render the above label as unknown. Furthermore, reasoning can get very fine-grained 
as the Contained Deletion ellipsis example \ref{ex:acd} below shows:

@@

In this paper, we concentrate on this sort of fine-grained, logical
reasoning. In particular, we present a logic-based system that deals
with many linguistic phenomena \emph{at the same time}. It is the
first system covering the sections on ellipsis and anaphora in the
FraCaS test suite and has the best coverage and accuracy on the
overall test suite.
% This is listed below; we can let the reader figure it out.
% \begin{itemize}
% \item A two-phase system (rather than a one-phase as described by
%   \citet{bernardy_type_2017}): a) using Haskell as a converter between
%   Grammatical Framework trees and Coq types, b) using various type
%   combinators to reach the desired NL semantics.
% \item The first run of the Anaphora and Ellipsis sections of the
%   FraCaS (based on work by \citet{bernardy_jolli})
%  \item  More coverage than any previous logical approach
%  \item State-of-the-art results in terms of accuracy compared to all
%    previous approaches, for every section of the FraCaS
%   \item Handing of multiple readings
%   \item  Threshold-based interpretation of (some) adjectives plus Linear arithmetic proofs
%   \item New handling of prepositions and adverbs compared to the
%     earlier system in \citet{bernardy_type_2017}, as well as new
%     handling of definitions, enabled by the dynamic semantics system.
%   \item Improvement over the previous treatment of Plurals/Quantifiers
%   \item Big improvement on the comparatives section enabled by
%     handling comparatives using a threshold (BUT one different to the
%     one used for adjectives). Again, the dynamic semantics system is
%     crucial here.
% \end{itemize}

@@

\providecommand\forcecenter{\multicolumn{1}{c}}
\providecommand\ncases[1]{{\ensuremath{^{#1}}}}
\begin{table}[hbt]
  \centering
  \small
\begin{tabularx}{\columnwidth}{Xr@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r}
Section      & {\kern -2em} \#cases & Ours     & FC & MINE & Nut  & Langpro  \\ \hline
Quantifiers  & 75          & .96  & .96    & .77  & .53  & .93  \\
             &             & \ncases{74}     &        &      &      &     \ncases{44} \\
Plurals      & 33          & .82      & .76    & .67  & .52  & .73 \\
      &          &       &     &   &   & \ncases{24} \\
Anaphora     & 28          & .86      &   -    & -    & -    &  -       \\
Ellipsis     & 52          & .87      &   -    & -    & -    &  -       \\
Adjectives   & 22          & .95 & .95    & .68  & .32  & .73 \\
             &          &  \ncases{20} &     &   &   &  \ncases{12} \\
Comparatives {\kern -1em}& 31          & .87      & .56    & .48  & .45  &  -       \\
Temporal     & 75          &  -       &   -    &   -  &  -   &  -       \\
Verbs        & 8           & .75      &   -    & -    & -    &  -       \\
Attitudes    & 13          & .92      & .85    & .77  & .46  & .92  \\ 
    &          &       &     &   &   & \ncases {9}  \\ \hline
Total        & 337         & .89      & .83    & .69  & .50  & .85  \\
             &             & \ncases{259}    & \ncases{174}  & \ncases{174}& \ncases{174}& \ncases{89}
  \end{tabularx}
  \caption{Accuracy of our system compared to others.
    ``Ours" refers to the approach presented in this paper. When a
    system does not handle the nominal number of test cases (shown in
    the second column), the actual number of test cases attempted is
    shown below the accuracy figure, in smaller font.  ``FraCoq''
    refers to the work of \citet{bernardy_type_2017}. ``MINE" refers
    to the approach of \citet{Mineshima:2015}, ``NUT" to the CCG
    system that utilizes the first-order automated theorem prover
    \textit{nutcracker} \cite{bos:2008}, and ``Langpro"
    to the system presented by \citet{Abzianidze:2015}. A dash
    indicates that no attempt was made for the section. }
  \label{tab:results}
\end{table}

>>>>

\begin{abstract}
  We present a system for Natural Language Inference which uses a
  dynamic semantics converter from abstract syntax trees to Coq
  types. It combines the fine-grainedness of a dynamic semantics
  system with the powerfulness of a state-of-the-art proof assistant. We evaluate the system on all sections of the FraCaS test
  suite, excluding section 6. This is the first system that does a
  complete run on the anaphora and ellipsis sections of the FraCaS. It
  has a better overall accuracy than any previous system.
\end{abstract}
\section{Introduction}
Natural Language Inference (NLI) is the task of determining of whether
an NL hypothesis H follows from an NL premise(s) P. NLI has received a
lot of attention in the Computational Semantics literature and has
been approached using a variety of techniques, ranging from logical
approaches
\citep{bos:2008,Mineshima:2015,Abzianidze:2015,bernardy:2017},
all the way to the recent Deep Learning (DL) models for NLI. The
latter approaches, following a general trend in NLP, have been
dominating NLI and a number of impressive results have been
produced \citep{kim:2018,radford:2018,liu:2019}.\footnote{These are
  the three systems with the best results on SNLI in increasing
  order at the time of writing.}  State-of-the-art DL systems achieve an accuracy of around
0.9 when tested on suitable datasets. However, the datasets that are
used are assuming a definition of inference that can be thought to be
`looser' or less precise compared to the definition assumed in
platforms based in logical approaches \citep{bernardy:2019}. For example, consider the following
 example  from the SNLI dataset, predominatly used to test DL
approaches:
%
\begin{lingex}
\item % An SNLI example \\
  \label{ex:snli}
\textbf{P}  A  man selling donuts to a customer during a world
exhibition event held in the city of Angeles. \\
 \textbf{H}  A woman drinks her coffee in a small cafe.\\
\textbf{Label: Contradiction} [SNLI]
% \item % An example from FraCaS\\
% \textbf{P1} A Scandinavian won the Nobel Prize.\\
% \textbf{P2}	Every Swede is  Scandinavian.\\
% \textbf{Q}  Did a Swede win the Nobel prize? \\
% \textbf{H} A Swede won the Nobel prize.\\
% \textbf{Label: Yes} [FraCaS 173]
\end{lingex}
%
In \ref{ex:snli}, a number of non-trivial
assumptions have to be made in order to arrive at a contradiction: a) the two
situations described have to be taken to refer to the same situation
in order to judge that the latter  contradicts the former, b)
the indefinite article in the premise has to be identified with the
indefinite article in the hypothesis. (Additionally considering that a
person cannot be a man selling donuts and a woman drinking coffee at
the same time.) While this can be part of the reasoning humans
perform, it is not the only possibility. More precise, logical
reasoning is also a possibility, and will render the above label as unknown. Furthermore, reasoning can get very fine-grained 
as the Contained Deletion ellipsis example \ref{ex:acd} below shows:

@@

In this paper, we concentrate on this sort of fine-grained, logical
reasoning. In particular, we present a logic-based system that deals
with many linguistic phenomena \emph{at the same time}. It is the
first system covering the sections on ellipsis and anaphora in the
FraCaS test suite and has the best coverage and accuracy on the
overall test suite.
% This is listed below; we can let the reader figure it out.
% \begin{itemize}
% \item A two-phase system (rather than a one-phase as described by
%   \citet{bernardy:2017}): a) using Haskell as a converter between
%   Grammatical Framework trees and Coq types, b) using various type
%   combinators to reach the desired NL semantics.
% \item The first run of the Anaphora and Ellipsis sections of the
%   FraCaS (based on work by \citet{bernardy_jolli})
%  \item  More coverage than any previous logical approach
%  \item State-of-the-art results in terms of accuracy compared to all
%    previous approaches, for every section of the FraCaS
%   \item Handing of multiple readings
%   \item  Threshold-based interpretation of (some) adjectives plus Linear arithmetic proofs
%   \item New handling of prepositions and adverbs compared to the
%     earlier system in \citet{bernardy:2017}, as well as new
%     handling of definitions, enabled by the dynamic semantics system.
%   \item Improvement over the previous treatment of Plurals/Quantifiers
%   \item Big improvement on the comparatives section enabled by
%     handling comparatives using a threshold (BUT one different to the
%     one used for adjectives). Again, the dynamic semantics system is
%     crucial here.
% \end{itemize}

@@

\providecommand\forcecenter{\multicolumn{1}{c}}
\providecommand\ncases[1]{{\ensuremath{^{#1}}}}
\begin{table}[hbt]
  \centering
  \small
\begin{tabularx}{\columnwidth}{Xr@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r}
Section      & {\kern -2em} \#cases & Ours     & FC & MINE & Nut  & Langpro  \\ \hline
Quantifiers  & 75          & .96  & .96    & .77  & .53  & .93  \\
             &             & \ncases{74}     &        &      &      &     \ncases{44} \\
Plurals      & 33          & .82      & .76    & .67  & .52  & .73 \\
      &          &       &     &   &   & \ncases{24} \\
Anaphora     & 28          & .86      &   -    & -    & -    &  -       \\
Ellipsis     & 52          & .87      &   -    & -    & -    &  -       \\
Adjectives   & 22          & .95 & .95    & .68  & .32  & .73 \\
             &          &  \ncases{20} &     &   &   &  \ncases{12} \\
Comparatives {\kern -1em}& 31          & .87      & .56    & .48  & .45  &  -       \\
Temporal     & 75          &  -       &   -    &   -  &  -   &  -       \\
Verbs        & 8           & .75      &   -    & -    & -    &  -       \\
Attitudes    & 13          & .92      & .85    & .77  & .46  & .92  \\ 
    &          &       &     &   &   & \ncases {9}  \\ \hline
Total        & 337         & .89      & .83    & .69  & .50  & .85  \\
             &             & \ncases{259}    & \ncases{174}  & \ncases{174}& \ncases{174}& \ncases{89}
  \end{tabularx}
  \caption{Accuracy of our system compared to others.
    ``Ours" refers to the approach presented in this paper. When a
    system does not handle the nominal number of test cases (shown in
    the second column), the actual number of test cases attempted is
    shown below the accuracy figure, in smaller font.  ``FraCoq''
    refers to the work of \citet{bernardy:2017}. ``MINE" refers
    to the approach of \citet{Mineshima:2015}, ``NUT" to the CCG
    system that utilizes the first-order automated theorem prover
    \textit{nutcracker} \cite{bos:2008}, and ``Langpro"
    to the system presented by \citet{Abzianidze:2015}. A dash
    indicates that no attempt was made for the section. }
  \label{tab:results}
\end{table}
